Blame and Coercion: Together Again for the Second Time

### 2019-10-16 paper.tex
applyCast for lazy UD blame calculus

\affiliation{
  \department{School of Informatics, Computing, and Engineering}              
  %% \department is recommended
  \institution{Indiana University}
  %% \institution is required
  \country{United States}
  %% \country is recommended
}
\email{kl13@iu.edu}          %% \email is recommended

\author{Jeremy Siek}

\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position2a}
  \department{Department2a}             %% \department is recommended
  \institution{Institution2a}           %% \institution is required
  \streetaddress{Street2a Address2a}
  \city{City2a}
  \state{State2a}
  \postcode{Post-Code2a}
  \country{Country2a}                   %% \country is recommended
}
\email{first2.last2@inst2a.com}         %% \email is recommended
\affiliation{
  \position{Position2b}
  \department{Department2b}             %% \department is recommended
  \institution{Institution2b}           %% \institution is required
  \streetaddress{Street3b Address2b}
  \city{City2b}
  \state{State2b}
  \postcode{Post-Code2b}
  \country{Country2b}                   %% \country is recommended
}
\email{first2.last2@inst2b.org}         %% \email is recommended

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
	Gradual Typing is great. Implementing gradually typed with blame tracking 
	and space efficiency is tricky. There exist two technique to do this: 
	coercion and threesome. Coercion is easy to understand, and easy enough to 
	implement, but difficult to reason about formally. Threesome is hard to 
	understand, easy to implement, and easy to reason about formally. We 
	propose hyper-coercion, which is easy to understand, as easy to implement 
	as coercion, and easy to reason about formally.
\end{abstract}

@@

@@

\figref{fig:blame-static} defines the syntax of blame calculus and its static 
semantics. It is little changed from previous definitions. 
The dynamic semantics of Blame Calculi depend on blame strategies, so we defer 
them to sub-sections.

@@

Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
Calculus in the style of CEK machines (\citet{felleisen1986control}). 
We conjecture that this CEK machines agree with the \lazyD{} blame calculus in 
\citet{siek2012interpretations}.
We will show in \hyperref{sec:hyper-coercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hyper-coercions.

@@

@@

  \fbox{$\mathit{applyCast}(v,c) = r$}
  \[
  \begin{array}{rclr}
    \mathit{applyCast}(v,c) = r
  \end{array}
  \]

\end{figure}

>>>>

\affiliation{
  \department{Computer Science Department}              
  %% \department is recommended
  \institution{Indiana University}
  %% \institution is required
  \country{United States}
  %% \country is recommended
}
\email{kl13@iu.edu}          %% \email is recommended

\author{Jeremy G. Siek}
\email{jsiek@indiana.edu}         %% \email is recommended

%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
%  \position{Position2a}
  \department{Computer Science Department}             %% \department is recommended
  \institution{Indiana University}           %% \institution is required
  \streetaddress{Street2a Address2a}
  %% \city{City2a}
  %% \state{State2a}
  %% \postcode{Post-Code2a}
  \country{United States}                   %% \country is recommended
}

\author{Andre Kuhlenschmidt}
\email{first2.last2@inst2a.com}         %% \email is recommended
\affiliation{
  \position{Position2b}
  \department{Department2b}             %% \department is recommended
  \institution{Institution2b}           %% \institution is required
  \streetaddress{Street3b Address2b}
  \city{City2b}
  \state{State2b}
  \postcode{Post-Code2b}
  \country{Country2b}                   %% \country is recommended
}
\email{first2.last2@inst2b.org}         %% \email is recommended

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  \todo[inline]{Rewrite this abstract based on the comparision table. -Jeremy}
  Gradual Typing is great. Implementing gradually typed with blame
  tracking and space efficiency is tricky. There exist two technique
  to do this: coercion and threesome. Coercion is easy to understand,
  and easy enough to implement, but difficult to reason about
  formally. Threesome is hard to understand, easy to implement, and
  easy to reason about formally. We propose hyper-coercion, which is
  easy to understand, as easy to implement as coercion, and easy to
  reason about formally.
  \todo[inline]{Spell it ``hypercoercion'' without the hyphen. -Jeremy}
\end{abstract}

@@

\listoftodos{}

@@

\figref{fig:blame-static} defines the syntax of blame calculus and its static 
semantics. It is little changed from previous definitions.
\todo[inline]{Which previous definitions are you refering to?
  What are the little changes? -Jeremy}
\todo[inline]{The term typing rule for casts is broken. -Jeremy}
The dynamic semantics of Blame Calculi depend on blame strategies, so we defer 
them to sub-sections.

@@

Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
Calculus in the style of CEK machines (\citet{felleisen1986control}).
\todo[inline]{The figure is too tall. You may need to pull some things
  out of the figure, such as the value typing. -Jeremy}
\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Explain why you are using a CEK machine instead of
  reduction semantics. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
  the value first and the cast second. -Jeremy}
\todo[inline]{The definition of values is too loose for a cast.
  You need to restrict the casts to just the inert ones. -Jeremy }
We conjecture that this CEK machines agree with the \lazyD{} blame calculus in 
\citet{siek2012interpretations}.
We will show in \hyperref{sec:hyper-coercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hyper-coercions.

@@

Fig.~\ref{fig:apply-Cast-UD}

@@

  Syntax
  \[
  \begin{array}{rclr}
    \stxrule{v}{values}{
      \cdots \mid 
      \vOOcast{v}{ \cOOcast{I}{l}{\star} } \mid
      \vOOcast{v}{ \cOOcast{P}{l}{P} }
    }
  \end{array}
  \]

  \fbox{$\mathit{applyCast}(v,c) = r$}
  \[
  \begin{array}{rclr}
    \mathit{applyCast}(v, \cOOcast{\star}{l}{\star} ) &=& v \\
    \mathit{applyCast}(v, \cOOcast{P}{l}{\star}) &=&
        v \langle \cOOcast{P}{l}{I} \rangle
          \langle \cOOcast{I}{l}{\star} \rangle
        & \text{if } I \sim P, I \neq P \\  
    \mathit{applyCast}(v, \cOOcast{\star}{l}{P}) &=&          
        v \langle \cOOcast{\star}{l}{I} \rangle
          \langle \cOOcast{I}{l}{P} \rangle
        & \text{if } I \sim P, I \neq P \\  
  \mathit{applyCast}(v \langle \cOOcast{I}{l}{\star} \rangle , \cOOcast{\star}{l}{I}) &=& v \\
  \mathit{applyCast}(v \langle \cOOcast{I_1}{l}{\star} \rangle , \cOOcast{\star}{l}{I_2}) &=& \rOOfail{l} & \text{if } I_1 \neq I_2 \\
  \mathit{applyCast}(v, \cOOcast{P_1}{l}{P_2}) &=&
     v \langle \cOOcast{P_1}{l}{P_2} \rangle & \text{if } P_1 \smile P_2
  \end{array}
  \]

  \caption{Definition of \textit{applyCast} for \lazyUD{}.}
  \label{fig:apply-Cast-UD}
\end{figure}

% the following are temporary -Jeremy
\clearpage
\pagebreak
